Looking for a Signal in the Noise: Revisiting Obesity and the microbiome

### 2016-03-05 Sze_ObesityMicrobiomeMeta_PeerJ_2016.Rmd
updated references

There has been a continuous stream of studies that report observing a link between the composition of microbiome and obesity. The first such study used genetically obese mice and observed that obese mice had a XXXXXer B/F ratio than lean mice [@Ley2005]. Translation of this result to humans by the same researchers did not observe this effect, but did find that obese individuals had a lower diversity than lean individuals [@turnbaugh_core_2009]. Since the publication of these studies there have been a steady stream of publications on the microbiome with associated BMI data but without clear explicit mention of any significant correlations between the microbiome and obesity [@ross_16s_2015; @zupancic_analysis_2012; @nam_comparative_2011; @arumugam_enterotypes_2011; @goodrich_human_2014; @yatsunenko_human_2012; @wu_linking_2011; @escobar_gut_2014]. Two re-analysis studies interrogated previously published microbiome and obesity data and concluded that the previously reported differences in community diversity and B/F among non-obese and obese individuals could not be generalized [@walters_meta-analyses_2014; @finucane_taxonomic_2014].

@@

* @ley2006 watched humans lose weight and communities change
* @turnbaugh20XX did fecal transplants (humans to mice) and transferred phenotype
* @ley20XX did fecal transplants (pregnant women to mice) and transferred phenotype

>>>>

There has been a continuous stream of studies that report observing a link between the composition of microbiome and obesity. The first such study used genetically obese mice and observed that obese mice had a lower Bacteroidetes and higher Firmicutes than lean mice (lower B/F ratio associated with obesity) [@ley_obesity_2005]. Translation of this result to humans by the same researchers did not observe this effect, but did find that obese individuals had a lower diversity than lean individuals [@turnbaugh_core_2009]. Since the publication of these studies there have been a steady stream of publications on the microbiome with associated BMI data but without clear explicit mention of any significant correlations between the microbiome and obesity [@ross_16s_2015; @zupancic_analysis_2012; @nam_comparative_2011; @arumugam_enterotypes_2011; @goodrich_human_2014; @wu_linking_2011; @escobar_gut_2014]. Two re-analysis studies interrogated previously published microbiome and obesity data and concluded that the previously reported differences in community diversity and B/F among non-obese and obese individuals could not be generalized [@walters_meta-analyses_2014; @finucane_taxonomic_2014].

@@

* [@ley_microbial_2006] watched humans lose weight and communities change
* [@turnbaugh_effect_2009] did fecal transplants (humans to mice) and transferred phenotype
* [@koren_host_2012] did fecal transplants (pregnant women to mice) and transferred phenotype
